The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$

### 2015-05-19 formalwriteup.tex
added lemmas in sections 2/3

The rational Cherednik algebra $\HH_{\hbar, c}(\h)$ admits a $\ZZ_{\geq 0}$-graded representation on the polynomial ring $A = \Sym(\h^*)$, known as the \textit{polynomial representation}. The actions of $\Sym(\h^*)$ and $k[S_n]$ on $A$ are by left multiplication and the $S_n$ action on $\h^*$, respectively.  The action of $\Sym(\h)$ is implemented by letting $y \in \h$ act via the \textit{Dunkl operator} $D_y$ defined by
\begin{align*}
D_y(f) = \hbar \partial_y f  - \sum_{k=0}^{n-1} \sum_{l=0}^{n-1} c  \langle y, x_k-x_l \rangle \frac{(1-s_{kl}) f}{x_k - x_l},
\end{align*}
where we note that $\frac{(1-s_{kl}) f}{x_k - x_l}$ is a polynomial for $f \in A$. Explicitly, for 
\[
D_i = 
\]
we have $D_{y_i - y_j} = D_i - D_j$.

@@

@@

Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that
\[
\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z} \text{ for all $0 \le i < n-1$}.
\]
We recall that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$ we have 
\begin{align*}
\frac{\partial F}{\partial x_i}%&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial x_i}\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).
\end{align*}
We define
\[
G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).
\]
Then we see that 
\[
\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).
\]
We can now calculate $\frac{\partial F_0}{\partial x_1},\frac{\partial F_0}{\partial x_0}$. 
\begin{align*}
\frac{\partial F_0}{\partial x_1}%&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_1(z)}{1-x_0z}\\
&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_1(z)}{1-x_0z}.\\
\frac{\partial F_0}{\partial x_0}%&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{z}{(1-x_0z)^2}F(z)+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
&=\frac{z}{1-x_0z}F_0(z)+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_0(z)}{1-x_0z}\\
%&=\frac{z}{1-x_0z}F_0(z)+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}\\
&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}.
\end{align*}
We note that $F_0(z)$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$. We see that 
\begin{align*}
\frac{1-s_{0i}}{x_0-x_i}(F_0)%&=\frac{1}{x_0-x_i}\left(\frac{F(z)}{1-x_0z}-\frac{F(z)}{1-x_iz}\right)\\
&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F(z)\\
%&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F(z)\\
%&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F(z)\\
&=\frac{z}{(1-x_iz)(1-x_0z)}F(z)\\
&=\frac{z}{1-x_iz}F_0(z).
\end{align*}
We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$. We consider $D_0F_0, D_1F_0$ separately first. We see that 
\[
D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)
\]
since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. We now compute
\begin{align*}
D_0F_0&=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}(F_0)\\
&=\frac{G_0(z)}{1-x_0z}+\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)-\sum_{j > 0} \frac{zc}{1-x_jz}F_0(z).\\
D_1F_0&=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_1}+c \frac{1-s_{01}}{x_0-x_1}(F_0)\\
&=\frac{G_1(z)}{1-x_0z}+\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{zc}{1-x_1z}F_0(z)\\
&=\frac{G_1(z)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0(z).
\end{align*}
It is then easy to see that 
\[
(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.
\]
In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_0}{\partial z}$.

We see easily that 
\[
\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.
\]
We now consider $\frac{\partial F}{\partial z}$. We compute
\begin{align*}
\frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\end{align*}
We define 
\[
V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\]
Then we see that 
\[
\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).
\]
From this it follows that
\begin{align*}
\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_0z}\right)\\
&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F(z)\\
&=\frac{V(z)}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_0}{(1-x_0z)^2} F(z)\\
&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).
\end{align*}
We now again consider $(D_1-D_0)(F_0)$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_0$ since that is $0$ in characteristic $p$. 
\begin{align*}
(D_1-D_0)(F_0)&=\frac{G_1(z)-G_0(z)}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\sum_{j} \frac{zc}{1-x_jz}F_0\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{zc}{1-x_jz}F_0\right)-nzcF_0\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{z-x_0z^2}{1-x_0z}F_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}F_0+\frac{zc}{1-x_jz}F_0\right)\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\left(\frac{x_0}{1-x_0z}F_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}F_0\right)\right)\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
&=\frac{G_1(z)-G_0(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.
\end{align*}
We consider $z^2V(z)$ and $G_i(z)$ for $i=0,1$. We note that $(g-1)^{p-1}$ divides $V(z)$ and $z(g-1)^{p-1}$ divides $G_i(z)$. Since the sum $\sum_{a=0}^{n-1} x_a$ is $0$, we see that $z^2 \mid g(z)-1$; therefore $z^{2p-2} \mid (g-1)^{p-1}$. Therefore $z^{p+1} \mid z^{2p-1} \mid G_i(z)$ and $z^{p+1} \mid z^{2p} \mid z^2V(z)$. (We note that $z^p \mid z^{2p-2} \mid V(z)$; this will be relevant later.)

>>>>

The rational Cherednik algebra $\HH_{\hbar, c}(\h)$ admits a $\ZZ_{\geq 0}$-graded representation on the polynomial ring $A = \Sym(\h^*)$, known as the \textit{polynomial representation}. In particular, for any $f \in A$ we can take a partial derivative $\frac{\partial f}{\partial x_i}$ by noting that $A=k[x_0,\dots,x_{n-2}]$ with $x_{n-1}=-x_0-\dots-x_{n-2}$; then we can write $f$ as a polynomial and take its partial derivative by any $x_i$ with $0 \le i \le n-2$.

The actions of $\Sym(\h^*)$ and $k[S_n]$ on $A$ are by left multiplication and the $S_n$ action on $\h^*$, respectively.  The action of $\Sym(\h)$ is implemented by letting $y \in \h$ act via the \textit{Dunkl operator} $D_y$ defined by
\begin{align*}
D_y(f) = \hbar \partial_y f  - \sum_{k=0}^{n-1} \sum_{l=0}^{n-1} c  \langle y, x_k-x_l \rangle \frac{(1-s_{kl}) f}{x_k - x_l},
\end{align*}
where we note that $\frac{(1-s_{kl}) f}{x_k - x_l}$ is a polynomial for $f \in A$. Explicitly, for 
\[
D_i = \hbar\frac{\partial f}{\partial x_i} -c \sum_{k \ne i} \frac{(1-s_{ki})f}{x_i-x_k}
\]
we have $D_{y_i - y_j} = D_i - D_j$.

@@

We begin by computing some partial derivatives of $F$ which will be useful for computing the action of the Dunkl operators.

\begin{lemma}\label{lem:dFdz} We have
\[
F'(z) = V(z) - \sum_{j=0}^{n-1} \frac{cx_j}{1-x_jz} F(z)
\]
such that $V(z)$ is a power series with $[z^l]V(z)=0$ for $l=0,\dots,p-1$. 
\end{lemma}

\begin{proof}
We see easily that 
\[
\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.
\]
We now consider $\frac{\partial F}{\partial z}$. We compute
\begin{align*}
\frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\end{align*}
We define 
\[
V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\]
It is then clear that 
\[
F'(z) = V(z) - \sum_{j=0}^{n-1} \frac{cx_j}{1-x_jz} F(z).
\]
Then it remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$. To show this, we need only show that $V(z)=z^pv(z)$ for some power series $v(z)$.

We consider the expansion of $g(z)$; this is $g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\left(\sum_i x_i\right)+z^2e_2(x_i)+\dots+z^ne_n(x_i)$ where $e_2,\dots,e_n$ are polynomials in the $x_i$. In particular we note that $\sum_i x_i=0$ by hypothesis, so $z^2 \mid g(z)-1$.

Then by the definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, so $z^{2p-2} \mid V(z)$. Since $p \ge 2$, it is clear that $z^p \mid V(z)$, so we can write $V(z)=z^pv(z)$ for some power series $v(z)$ as desired. 
\end{proof}

\begin{lemma}\label{lem:dFdxi} For any $0 \le i < n-1$ we have 
\[
\frac{\partial F}{\partial x_i} = G_i(z) - \left(\frac{zc}{1-x_{n-1}z}-\frac{zc}{1-x_iz}\right)F(z)
\]
such that $G_i(z)$ is a power series with $[z^l]G_i(z)=0$ for $l=0,\dots,p$. 
\end{lemma}

\begin{proof}

Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that
\[
\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z} \text{ for all $0 \le i < n-1$}.
\]
Then we see that for all $0 \le i < n-1$ we have 
\begin{align*}
\frac{\partial F}{\partial x_i}%&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial x_i}\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).
\end{align*}
We define
\[
G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).
\]
Then we see that
\[
\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).
\]

Then it remains only to show that $[z^l]G_i(z)=0$ for $l=0,\dots,p$. To show this, we need only show that $G_i(z)=z^{p+1}g_i(z)$ for some power series $v(z)$.

We consider the expansion of $g(z)$; this is $g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\left(\sum_i x_i\right)+z^2e_2(x_i)+\dots+z^ne_n(x_i)$ where $e_2,\dots,e_n$ are polynomials in the $x_i$. In particular we note that $x_{n-1}=-x_0-\dots-x_{n-2}$ by hypothesis, so $z^2 \mid g(z)-1$.

Then by the definition of $G_i(z)$, we see that $z(g-1)^{p-1} \mid G_i(z)$, so $z^{2p-1} \mid V(z)$. Since $p \ge 2$, it is clear that $z^{p+1} \mid G_i(z)$, so we can write $G_i(z)=z^{p+1}g_i(z)$ for some power series $g_i(z)$ as desired.

\end{proof}

@@

By Lemma~\ref{lem:dFdxi} we note that for $i=0,1$ we have $\frac{\partial F}{\partial x_i} = G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z)$ for power series $G_i(z)$ with $[z^l]G_i(z)=0$ for $l=0,\dots,p$.

We can now calculate $\frac{\partial F_0}{\partial x_1},\frac{\partial F_0}{\partial x_0}$. We compute
\begin{align*}
\frac{\partial F_0}{\partial x_1}%&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_1(z)}{1-x_0z}\\
&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_1(z)}{1-x_0z}.\\
\frac{\partial F_0}{\partial x_0}%&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{z}{(1-x_0z)^2}F(z)+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
&=\frac{z}{1-x_0z}F_0(z)+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_0(z)}{1-x_0z}\\
%&=\frac{z}{1-x_0z}F_0(z)+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}\\
&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}.
\end{align*}
We note that $F_0(z)$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$. We see that 
\begin{align*}
\frac{1-s_{0i}}{x_0-x_i}(F_0)%&=\frac{1}{x_0-x_i}\left(\frac{F(z)}{1-x_0z}-\frac{F(z)}{1-x_iz}\right)\\
&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F(z)\\
%&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F(z)\\
%&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F(z)\\
&=\frac{z}{(1-x_iz)(1-x_0z)}F(z)\\
&=\frac{z}{1-x_iz}F_0(z).
\end{align*}
We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$. We consider $D_0F_0, D_1F_0$ separately first. We see that 
\[
D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)
\]
since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. We now compute
\begin{align*}
D_0F_0&=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}(F_0)\\
&=\frac{G_0(z)}{1-x_0z}+\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)-\sum_{j > 0} \frac{zc}{1-x_jz}F_0(z).\\
D_1F_0&=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_1}+c \frac{1-s_{01}}{x_0-x_1}(F_0)\\
&=\frac{G_1(z)}{1-x_0z}+\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{zc}{1-x_1z}F_0(z)\\
&=\frac{G_1(z)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0(z).
\end{align*}
It is then easy to see that 
\[
(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.
\]
In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_0}{\partial z}$.

We recall by Lemma~\ref{lem:dFdz} that
\[
\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).
\]
where $[z^l]V(z)=0$ for $l=0,\dots,p-1$.

From this it follows that
\begin{align*}
\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_0z}\right)\\
&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F(z)\\
&=\frac{V(z)}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_0}{(1-x_0z)^2} F(z)\\
&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).
\end{align*}
We now again consider $(D_1-D_0)(F_0)$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_0$ since that is $0$ in characteristic $p$. 
\begin{align*}
(D_1-D_0)(F_0)&=\frac{G_1(z)-G_0(z)}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\sum_{j} \frac{zc}{1-x_jz}F_0\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{zc}{1-x_jz}F_0\right)-nzcF_0\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{z-x_0z^2}{1-x_0z}F_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}F_0+\frac{zc}{1-x_jz}F_0\right)\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\left(\frac{x_0}{1-x_0z}F_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}F_0\right)\right)\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
&=\frac{G_1(z)-G_0(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.
\end{align*}

We note that $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is a linear combination of $[z^l](G_1(z)-G_0(z)+z^2V(z))$ for $0 \le l \le p$. This means that $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is a linear combination of $[z^l]G_0(z)$ for $0 \le l \le p$, $[z^l]G_1(z)$ for $0 \le l \le p$, and $[z^l]V(z)$ for $0 \le l \le p-2$. By Lemmas~\ref{lem:dFdz} and \ref{lem:dFdxi} we recall that the coefficients of $G_i(z),V(z)$ under consideration are all $0$. This implies that $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)=0$. Therefore
\[
[z^p]\left((D_1-D_0)(F_0)\right)=[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right).
\]
Let $b=[z^{p-1}](F_0)$. We see that $[z^p](-zF_0)=-b$. Then $[z^{p-2}]\left(\frac{\partial F_0}{\partial z}\right)=(p-1)b=-b$, so $[z^p]\left(-z^2\frac{\partial F_0}{\partial z}\right)=b$. Therefore $[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right)=-b+b=0$, so 
\[
[z^p]((D_1-D_0)(F_0))=(D_1-D_0)([z^p]F_0)=(D_1-D_0)f_0=0.
\]
By the symmetry of the $F_i$, this is the only Dunkl operator we need consider; it is clear that all the $f_i$ are killed by the Dunkl operators.
\end{proof}
